\documentclass[fleqn,10pt]{olplainarticle}
% Use option lineno for line numbers 

\title{Preparatory Material for AI/ML Job Interviews}

\author[1]{Muhammad Ahmed Shah}
\affil[1]{Language Technologies Institute, Carnegie Mellon University}

\keywords{Machine Learning, Artificial Intelligence, Interview, Apple, Amazon}

\begin{abstract}
This document is a digitized compilation of the notes I made while preparing for interviews for the Applied Scientist in the Alexa Speech team at Amazon and Multi-Modal Machine Learning Engineer position in the Siri team at Apple in May 2020. While I interviewed at only these two companies, my notes are not tailored to their interview process, but rather consist of basic concepts from statistics, machine learning and deep learning. Therefore, I believe that these notes can serve as a resource to prepare for AI/ML interviews at most companies, or even to just review fundamental concepts. In addition to the technical notes, this document includes brief accounts of my interview experience with both companies. My objective in compiling this document is two-fold: (1) to preserve these notes for my own review in the future if (or rather \textit{when}) the pages they are written on are lost and (2) to share this resource with the wider community so that other students, researchers and practitioners may be able to benefit from it.
\end{abstract}

\begin{document}

\flushbottom
\maketitle
\thispagestyle{empty}

\section{Introduction}

Thanks for using Overleaf to write your article. Your introduction goes here! Some examples of commonly used commands and features are listed below, to help you get started.

\bibliography{refs}

\end{document}